### 2011-05-06 paper/paper.tex

\begin{theorem}
Any Markov chain whose state space is an open subset of $\subset\mathbb{R}^n$ with a symmetric transition distribution has the uniform distribution as a stationary distribution.
\end{theorem}
\begin{proof}
We will let $S$ be the set of all states of the chain. Furthermore, let $\mu$ be the uniform distribution on $S$, i.e. $\mu(x) = \frac{1}{\text{Vol}(S)}$. Then we want to show that for every subset $A \subseteq S$, $\int_A (\mu P)(y)\, dy = \frac{\text{Vol}(A)}{\text{Vol}(S)}$. To do this, notice the following:
\begin{align*}
\int_A (\mu P)(y)\, dy &= \int_A \int_S \mu(x)P(x,y)\, dx\, dy \\
&= \int_S \int_A \mu(y)P(y,x)\, dy\, dx
\end{align*}
where here we have used the fact that $\mu(x) = \mu(y)$, $P(x,y) = P(y,x)$, and that we can interchange the order of integration by Fubini's theorem because the double integral is a probability, and therefore finite and the integrand is always positive. However, we can see that this last quantity is the probability of starting at a point in $A$ and moving to a point in $S$. Since we will always move to a point in $S$, that quantity is just the probability that we start in $A$, which is simply $\int_A \mu(y)\, dy = \frac{\text{Vol}(A)}{\text{Vol}(S)}$, as desired.
\end{proof}
\begin{remark} 
\emph{This is a continuous analog of the following fact: given an undirected $d$-regular graph $G$, consider a Markov chain which, from any vertex, jumps to each of its neighbors with probability $1/d$. Then the stationary distribution on this Markov chain is the stationary distribution.}
\end{remark}

>>>>

\begin{theorem}
Any Markov chain whose state space is an open subset of $\mathbb{R}^n$ with a symmetric transition distribution has the uniform distribution as a stationary distribution.
\label{symmetric}
\end{theorem}
\begin{proof}
We will let $S$ be the set of all states of the chain. Furthermore, let $\mu$ be the uniform distribution on $S$, i.e. $\mu(x) = \frac{1}{\text{Vol}(S)}$. Then we want to show that for every subset $A \subseteq S$, $\int_A (\mu P)(y)\, dy = \frac{\text{Vol}(A)}{\text{Vol}(S)}$. To do this, notice the following:
\begin{align*}
\int_A (\mu P)(y)\, dy &= \int_A \int_S \mu(x)P(x,y)\, dx\, dy \\
&= \int_S \int_A \mu(y)P(y,x)\, dy\, dx
\end{align*}
where here we have used the fact that $\mu(x) = \mu(y)$, $P(x,y) = P(y,x)$, and that we can interchange the order of integration by Fubini's theorem because the double integral is a probability, and therefore finite and the integrand is always positive. However, we can see that this last quantity is the probability of starting at a point in $A$ and moving to a point in $S$. Since we will always move to a point in $S$, that quantity is just the probability that we start in $A$, which is simply $\int_A \mu(y)\, dy = \frac{\text{Vol}(A)}{\text{Vol}(S)}$, as desired.
\end{proof}
\begin{remark} 
\emph{This is a continuous analog of the following fact: given an undirected $d$-regular graph $G$, consider a Markov chain which, from any vertex, jumps to each of its neighbors with probability $1/d$. Then the stationary distribution on this Markov chain is the stationary distribution.}
\end{remark}
